\section[Smartphones]{Smartphone Sicherheit}

\begin{frame}{}
  \begin{center}
    \structure{\Large \insertsection}
  \end{center}
\end{frame}


\begin{frame}{Smartphones}
  \begin{itemize}
	  \item immer dabei
	  \item sammeln viele Daten über Benutzer und Umgebung
	  \begin{itemize}
	  \item Standort
	  \item Anruflisten
	  \item Kontakte
	  \item Email
	  \item SMS
	  \item Logins (Facebook, Whatsapp, etc)
	  \item Fotos/Videos, auch Thumbnails
	  \item Browserverlauf
	  \item ...
	  \end{itemize}
  \end{itemize}

\end{frame}

\begin{frame}{Probleme}
  \begin{itemize}
    \item immer mehr im Fokus von Viren/Malware/Phishing etc.
    \item aber auch Diebstahl/Verlust
    \item Zugriffsrechte von Apps (v.a. Jailbreak/Root)
  \end{itemize}
\end{frame}

\begin{frame}{Online TSP}
  \begin{itemize}
    \item TSP: new requests arise while ``on the road''
    \item adds \emph{time} as a new factor
    \item not comparable with ``pure'' TSP
    \item corresponding offline problem: \emph{TSP with release dates}
  \end{itemize}
\end{frame}

\begin{frame}{TSP-RD}
  \begin{block}{Definition: TSP-RD}
    In a \alert{TSP with Release Dates}, find a round-trip tour stating at the origin, s.t. all cities are visited exactly once \emph{after their release date}.
  \end{block}
  Preliminaries:
  \begin{itemize}
    \item $n$ Cities; $N=\{1, ... ,n\}; i \in N $
    \item Cities have a location ($l_i$) in a metric space.
    \item Cities are revealed at their disclosure date ($q_i \ge 0$).
    \item Cities are ready for service at their release date ($r_i \ge q_i$).
    \item The service time at each city is 0.
    \item The salesman travels at constant speed (1 unit of distance per unit of time) or is idle.
    \item The problem begins at time 0 and the salesman is idle at the origin ($i=0$).
  \end{itemize}
\end{frame}

\begin{frame}{TSP-RD on $\Bbb{R}^+$}
  Consider cities with location in $\Bbb{R}^+$ (non-negative real line)

  \vspace{5pt}
  \begin{block}{Optimal Offline Algorithm}
    \begin{enumerate}
      \item Go directly to to city $l_{max} = max_{i \in N}\{l_i\}$.
      \item Wait at city $l_{max}$ for $max_{i \in N}\{max\{0,r_i - 2l_{max}+l_i\}\}$.
      \item Proceed directly back to the origin, visiting the cities.
    \end{enumerate}
  \end{block}

  \begin{block}{Remark}
    The offline algorithm can ignore the disclosure dates $q_i$, because it knows the data in advance!
  \end{block}

  $C_{OPT}(n) = 2l_{max} + max_{i \in N}\{max\{0,r_i - 2l_{max}+l_i\}\}$
  \note{blackboard demo}
\end{frame}

\begin{frame}{Online TSP-RD on $\Bbb{R}^+$}
  Online algorithms
  \begin{itemize}
    \item need to consider disclosure dates $q_i$
    \item don't know final value of $n$
  \end{itemize}
  \vspace{5pt}

  \begin{block}<2->{Move-Right-If-Necessary Algorithm}
    consider $q_i=r_i$
    \begin{enumerate}
      \item If there is an unserved city to the right, move toward it.
      \item If there are no unserved cities to the right, move toward the origin.
      \item Become idle at the origin.
    \end{enumerate}
  \end{block}

  \begin{Theorem}<3->
    $C_{MRIN}(n) \le \frac {3}{2} C_{OPT}(n), \forall n$.
  \end{Theorem}

  \note{blackboard demo}
\end{frame}

\begin{frame}{Online TSP-RD on $\Bbb{R}^+$}

  \begin{block}{Move-Left-If-Beneficial Algorithm}
    consider $q_i \le r_i$
    \begin{enumerate}
      \item If there is an unserved city to the right, move toward it.
      \item If there are no unserved cities to the right, move toward the origin \alert{iff} we can visit all unserved cities on/after their release date; otherwise stay idle at the current position.
      \item Become idle at the origin.
    \end{enumerate}
  \end{block}

  \begin{block}{Remark}
    If $q_i = r_i$, MLIB is indistinguishable from MRIN!\\
    If $q_i = 0$, MLIB is indistinguishable from the offline algorithm!
  \end{block}

  \note{blackboard demo}
\end{frame}

\begin{frame}{Online TSP-RD on generic metric space}
  Additions to the problem:
  \begin{itemize}
    \item locations in a generic metric space (e.g., Euclidean Plane)
    \item distance function $d(\cdotp,\cdotp)$, 
    \item Origin $o$
    \item availability of a ``black box'' algorithm solving offline TSP-RD
  \end{itemize}
  \vspace{5pt}

  \begin{block}{Plan-At-Home-with-disclosure-dates Algorithm}
    \begin{enumerate}
      \item Whenever at origin, follow a tour that serves all cities whose disclosure dates have passed.
      \item If at time $q_i$ the server is at position $p$ and a new request arrives at location $x$, then
      \begin{itemize}
        \item if $d(x,o) > d(p,o)$, go back to origin, continue with (1).
        \item if $d(x,o) \le d(p,o)$, ignore it.
      \end{itemize}
    \end{enumerate}
  \end{block}
\end{frame}

\begin{frame}{PAH-dd}
  \begin{Theorem}
    Algorithm PAH-dd is 2-competitive
  \end{Theorem}
  \begin{Proof}
    part. proof (for case 1);\\
    $T$ is optimal tour length at time $q_n$ from ``black box'' alg.
    \begin{small}
    \begin{align}
      C_{PAH-dd} & =  q_n + T \\
		 &\le r_n + T \\
		 &\le C_{OPT} + T \\
		 &\le C_{OPT} + C_{OPT} \\
		 &\le 2* C_{OPT}
    \end{align}
    \end{small}
  \end{Proof}
\end{frame}

\begin{frame}{PAH-dd}
  \begin{Proof}
    part. proof (for case 2a);\\
    $d(o,l_n)<d(o,p(q_n))$ \\
    implies: arrive at $o$ before $q_n + d(o,l_n)$
    \begin{small}
    \begin{align}
      C_{PAH-dd} &  < q_n + d(o,l_n) + T \\
		 &\le r_n + d(o,l_n) + T \\
		 &\le C_{OPT} + T \\
		 &\le C_{OPT} + C_{OPT} \\
		 &\le 2* C_{OPT}
    \end{align}
    \end{small}
  \end{Proof}
\end{frame}

\begin{frame}{PAH-dd}
  \begin{Proof}
    part. proof (for case 2b) omitted
  \end{Proof}

  \begin{block}{Remark}
    By assuming, that $q_i = r_i - a$, and $\alpha = \frac{a}{L_{TSP}}$, it can be shown, that PAH-dd is $(2-\frac{\alpha}{1+\alpha})$-competitive.\\
    (This resolves to $a/L_{TSP}+a)$, thus with $a \sim L_{TSP}$ PAH-dd is $\frac{3}{2}$-competitive.
  \end{block}
\end{frame}

\begin{frame}{TSP Competitiveness Examples}
  For TSP without disclosure-dates $q_i \le r_i$
  \begin{itemize}
    \item on metric space: 2-competitive
    \item polynomial on metric space: 2.78-competitive
    \item on $\Bbb{R}$: 1.64-competitive
    \item on $\Bbb{R}^+$: 1.5-competitive
  \end{itemize}
\end{frame} 
